\section{Requests}

\subsection{Neutrino beam}
The experiment can run parasitically with T2K, therefore we request no dedicated beam time nor beam condition.
As data taking periods, we request the `nominal' T2K one-year operation both for the neutrino beam and the antineutrino beam.
The T2K has been requesting $0.9\times10^{21}$~POT/year and actually accumulating about $0.7\times10^{21}$~POT/year in recent years.
For each year, starting from the Autumn,  T2K is running predominantly in the neutrino mode or in the antineutrino mode.
Our request is to have one-year neutrino-mode data and another one-year antineutrino mode data
assuming that the POT for the fast extraction in each year is more than $0.5\times10^{21}$~POT.

\subsection{Equipment request including power line}
We request the followings in terms of equipment on the B2 floor:
\begin{itemize}
\item Site for the WAGASCI modules, Side-MRD modules and BabyMIND and their electronics system on the B2 floor of the near detector hall (Fig. \ref{fig:location}).
\item Anchor points (holes) on the B2 floor to secure the WAGASCI modules, Side-MRD module and Baby-MIND (Fig. \ref{fig:floor_plan})
\item Power line for the magnets in Baby-MIND: 400 V tri-phase 48-to-62 Hz, capable of delivering 12 kW.
\item Electricity for electronics and water circulation system, 3 kW, standard Japanese electrical sockets.
	\begin{enumerate}
		\item Online PCs: 2.1 kW
		\item Electronics: 0.7 kW
		\item Water sensors: ?
	\end{enumerate}
\item Air conditioner for cooling heat generation at Baby-MIND magnets, online PCs and electoronics
\item Beam timing signal and spill information
\item Network connection
\end{itemize}


\subsubsection{Baby MIND Equipment request including power line}
We request the following in terms of equipment on the B2 floor:
\begin{itemize}
\item{Site for the Baby MIND detector and its electronics systems on the B2 floor of the near detector hall.}
\item{Anchor points (holes) on the B2 floor to secure the 9 support frames, of order 4 holes per frame, detailed floor plans to be communicated in a separate document.}
\item{Power line for the magnet: 400 V tri-phase 48-to-62 Hz, capable of delivering 12 kW. We have a wish for the magnet power line to be installed and available to us by beginning of March 2018.}
\item{Electricity for electronics, 1 kW, standard Japanese electrical sockets.}
\item{Beam timing signal and spill information}
\item{Network connection}
\end{itemize}
The infrastructure for much of the above exists already, and will be shared in part with the WAGASCI experiment. Exceptions are the power line for the magnet and holes in the B2 floor to anchor the detector support structures.
